---
title: "The Causal Effect of Temperature on Average Trip Duration (TWFE Model)"
author: "Mai Nguyen"
date: "`r Sys.Date()`"
output: html_document
---

```{r load packages}

library('dplyr')
library('readr')
library('plm')
library('stargazer')
library('parameters')
```

## 1. Load Data

```{r load_data}
# --- 1. Load Data ---
# Load the regular dataset
trip.data <- read.csv("data/trips_cleaned.csv")
# Load the panel dataset into a dataframe called 'bike.panel'
trip.panel <- read.csv("data/trips_panel.csv")

# --- 2. Set index ---
trip.panel <- pdata.frame(crime, index=c('neighborhood_id', 'day'))
head(trip.panel)
```

## 2. Estimate Panel Models

Here we run our panel regressions:
1. **Regular OLS** (not shown here) - does not control for neighborhood or day of the year fixed effects.
2. **Fixed Effects Models:**
  1.  **Within Estimator:** Controls *only* for neighborhood.
  2.  **Two-Way FE (TWFE):** Controls for both neighborhood (`model="within"`) and day of the week (`factor(day_of_week_num)`). **This is your target model.**
  3.  **First Differences (FD):** An alternative to fixed effects.

```{r panel_models}
# --- 6. Estimate Models ---

# Model 1: Regular OLS (for comparison)
ols_model <- lm(avg_trip_minutes ~ day_mean_temperature + day_mean_wind_speed + day_total_precipitation + holiday,
                    data=trip.data)
summary(ols)

# Model 2: Fixed effects or 'within' estimator 
within_model <- plm(avg_trip_minutes ~ day_mean_temperature + day_mean_wind_speed + day_total_precipitation + holiday,
                    data=trip.panel,
                    model='within')
summary(within_model)

# Model 3: First Differences Model
fd_model <- plm(avg_trip_minutes ~ day_mean_temperature + day_mean_wind_speed + day_total_precipitation + holiday, 
                  data=trip.panel, 
                  model="fd")
summary(fd_model)

# Model 4: Least square dummy variables 
# Different regression lines with the same slope, different intercepts
lsdv_model <- plm(avg_trip_minutes ~ day_mean_temperature + day_mean_wind_speed + day_total_precipitation + holiday
                  + neighborhood_id - 1, 
                  data=trip.panel, 
                  model="pooling")
summary(lsdv_model)

# Model 5: Two-Way Fixed Effects (TWFE) Model
twfe_model <- plm(avg_trip_minutes ~ day_mean_temperature + day_mean_wind_speed + day_total_precipitation + holiday + factor(day), 
                  data=trip.panel, 
                  model="within")
summary(twfe_model)
```

## 3. Compare Models with Stargazer

This chunk uses `stargazer` to create a beautiful comparison table of all the models we just ran. The `type="html"` argument will make it render nicely in the notebook.

```{r stargazer, results='asis'}
# --- 7. Compare Models with Stargazer ---
# Outline the output to a nicer format
stargazer(ols_model, within_model, fd_model, lsdv_model, twfe_model, type="text", 
          dep.var.labels=c("OLS", "Fixed effects", "First diffs", "LSDV", "TWFE"), 
          covariate.labels=c("temperature", "wind speed", "precipitation", "holiday"), 
          out = "trip_results.txt")
```
